% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{multicol}


%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}
\center{\huge{\textbf{Clement Jambou}}}
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

    &+1 505 557 7745 (USA) \\
  & clem.jambou@gmail.com \\

\end{tabular*}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\resheading{Personal Statement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \begin{center}
%  \parbox{6.762in}{I'm the hardest working person I know, and therefore you should hire me. My qualities include blah, blah, and blah. I have lots of experience working with blah, and I am not afraid to blah. In fact, I'm such an amazing person that I can't believe you haven't hired me yet.}
%  \end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work and Research Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}


\item
\ressubheading{CEO and Co-founder at Unsupervised.ai}{San Francisco/Shenzhen/Paris}{}{2016-2020}
Building Robots for Warehouses and Factories
\begin{itemize}
    \item \textbf{Team} Hired and managed a team of up to 8 engineers, technicians and designer between SanFrancisco, Shenzhen and Paris.
    \item \textbf{Self-driving stack} Built a self-driving stack for Mobile autonomous robots, including SLAM,AMCL, and behavioral planning.  Leveraged multiple state of the art tools including ROS,Python (Flask, Pandas, Numpy), React, MongoDb/DynamoDb.
    \item \textbf{Production}: Built a product from scratch including prototyping (Mechanical, Electrical andSoftware) to 30-unit batch production and assembly.
    \end{itemize}

    \item
\ressubheading{Senior Data Scientist at Lyft}{San Francisco}{}{2014-2016}
    Marketplace Growth team, helped grow the team from 4 to more than 20 Data Scientists. Mapping/Self Driving team.
    \begin{itemize}
        \item \textbf{Simulation} Build Simulation tool, used to guide business decision and optimize Marketplace algorithms, used by DS team daily.
        \item \textbf{Dispatch} Algorithm: prediction and decision for optimal use of available drivers
        \item \textbf{Dynamic Pricing}: real time price multiplier that account for demand prediction and available supply, to deliver optimal service.
        \item Lyft Line \textbf{Matching} Algorithm: Match the passengers that have a similar route together, optimization of the dispatch decision to maximize sustainable discount compared to a classic ride.
        \item \textbf{ETA prediction} Build state of the art performing ETA prediction model using Deep Neural Network.
        \item \textbf{SLAM / Mapping} Build a scalable 3D mapping tool using Velodyne LIDAR and IMU/GPS.
        \end{itemize}

    \item
\ressubheading{Data Scientist Intern at Lyft}{San Francisco}{}{Summer 2013}
    \begin{itemize}
        \item Modelization and Implementation of a positioning system to coach ride-sharing driver toward a better destination, using real-time demand and traffic estimation to minimize the time between two rides for a driver.
        \item Experience with \textbf{Python}, \textbf{MongoDB}, parallelization and production on \textbf{Heroku}
    \end{itemize}


    \item
\ressubheading{Imperial College London}{Department of Computing}{}{2013 - 2014}
    \begin{itemize}

        \item Research Project in Machine Learning and Optimization : " \textbf{Learning walking skills for modular Robots}"
        \item Master's Thesis : Learning Music Representation using Recurrent Neural Networks and other Deep Learning Techniques (Summer 2014)
    \end{itemize}



\item
	\ressubheading{ISAE-Supaero, Bachelor project}{Mathematics, Control and Computer Science Department}{}{June 2012}
		\begin{itemize}
\item Design, programming and manufactoring of 4 devices for the 2012 Edition of the ASME Student Design Competition (American Society of Mechanical Engineers). The devices had to compete automatically an "Energy Relay" using differents energy sources for propulsion.
	\end{itemize}


\item
	\ressubheading{European Space Agency}{Noordwijk, Netherlands}{ Intern at the European Space Research and Technology Center (ESTEC)}{July 2012}
\vspace{0.2cm}

Telerobotics and Haptics laboratory:
	\begin{itemize}
		\resitem{Design of the covers of the X-Arm 2.0 Exoskeleton for its future use on board of the International Space Station }
	\end{itemize}
\end{itemize}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item
	\ressubheading{Imperial College of London, Department of Computing}{London, England}{Master of Science in Advanced Computing}{2013 - 2014}

\item
	\ressubheading{Institut Superieur de l'Aeronautique et de l'Espace}{Toulouse, France}{Supaero Graduate Program}{2011 - 2014}
	\begin{itemize}
		\resitem{BS in 2012}
		\resitem{Major in Computer Science}
	\end{itemize}

\item
	\ressubheading{Lycee Hoche}{Versailles, France }{ }{2009-2011}

	\textit{Undergraduate Program in Mathematics, Physics and Computer Science
 for the \newline competitive exams  to the french "Grandes Ecoles" (top 7 \%)}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Awards \& Honors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\textit{(Details attached in the Awards list.)}
	\vspace{-2pt}
	\begin{center}\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
        \multicolumn{2}{c}{Speaker at PyData Paris  \cftdotfill{\cftdotsep}2015}\\
		\multicolumn{2}{c}{$1^{st}$ prize of the Student Design Robotics Competition of the ASME  \cftdotfill{\cftdotsep}2012}\\
		\multicolumn{2}{c}{$1^{st}$ European prize at the Old Guard Oral Presentation Competition \cftdotfill{\cftdotsep} 2012}\\
	 %	Merit-based Scholarship as financial support for a Master's in the United States from 				SUPAERO\\
	%	\multicolumn{2}{c}{ alumni association (\$10,000)\cftdotfill{\cftdotsep}2012}\\
		\multicolumn{2}{c}{Junior Fermat Prize in Mathematics  \cftdotfill{\cftdotsep}2010}\\
		\multicolumn{2}{c}{$1^{st}$ Prize with the French team for the International Tournament of Young Mathematicians\cftdotfill{\cftdotsep}2010}\\
		\multicolumn{2}{c}{$2^{nd}$ Prize of the academy of Versailles for Mathematics Olympiads  \cftdotfill{\cftdotsep}2008}\\
		\vphantom{E}
\end{tabular*}
\end{center}\vspace*{-16pt}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{2}
\subsection*{Computer skills}
\begin{itemize}
\item \textbf{Languages :} Python 2/3 (Pandas, Numpy, Theano, Tensorflow), C/C++ (OpenCv), Javascript(React + Graphql) Java, Caml, Delphi, XHTML/CSS, PHP/MySQL
\item \textbf{Software :}  Latex, Photoshop, 3D-CAD with CATIA, Fusion360, Maple, Matlab
\item \textbf{Teamwork :}  Git (Github)
\item \textbf{OS :} Linux, Unix, Windows %, ROS(Robotics)
\end{itemize}

\subsection*{Languages}
\begin{itemize}
\item \textbf{French} \textit{native language}
\item \textbf{English} \textit{proficient ( Toefl-IBT : 105/120)}
\item \textbf{German} \textit{proficient (Abitur Diploma)}
\end{itemize}
\vspace*{0.1cm}
\end{multicols}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Interests}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item \textbf{Music :} Cello, Guitar
\item \textbf{Sports :} Athletics (Marathon : 2h53 ), Soccer, Mountaineering, Climbing
\item \textbf{Campus Activities :} President of the Micro-drones club and Member of the Robotics Club at ISAE and Member of the Robotics Club at ICL
\end{itemize}
\end{document}
